Reproducible development environments with rix

### 2023-12-23 paper.qmd
expression that install latest R

As an alternative to the above approach, I will present the [Nix]{.proglang}
package manager, which available for all major operating system and focuses on
installing and building software in a reproducible manner. To make
[Nix]{.proglang} more accessible to [R]{.proglang} programmers, we developed the
[rix]{.pkg} which we will present in this article.

@@

>>>>

As an alternative to the above approach, we will present the [Nix]{.proglang}
package manager, which available for all major operating system and focuses on
installing and building software in a reproducible manner. To make
[Nix]{.proglang} more accessible to [R]{.proglang} programmers, we developed the
[rix]{.pkg} which we will present in this article.

@@

Nix expressions are written in the [Nix]{.proglang} programming language,
which is a purely functional programming language. Here is a simple expression
that builds a shell environment containing version 4.3.1 of R:

```{r, echo = F}
library(rix)

rix(r_ver = "4.3.1",
    project_path = tempdir(),
    print = TRUE)
```
